---
title: 'What comes next'
teaching: 10
exercises: 2
---

:::::::::::::::::::::::::::::::::::::: questions 

- How do you write a lesson using R Markdown and `{sandpaper}`?
- How do you make sure you understand everything?
- How do you edit things out?

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Explain how to use markdown with the new lesson template
- Demonstrate how to include pieces of code, figures, and nested challenge blocks
- Try out editing things yourself

::::::::::::::::::::::::::::::::::::::::::::::::

## Introduction

This is a lesson created via The Carpentries Workbench. It is written in
[Pandoc-flavored Markdown][pandoc] for static files (with extension `.md`) and
[R Markdown][r-markdown] for dynamic files that can render code into output
(with extension `.Rmd`). Please refer to the [Introduction to The Carpentries
Workbench][carpentries-workbench] for full documentation.

What you need to know is that there are three sections required for a valid
Carpentries lesson template:

 1. `questions` are displayed at the beginning of the episode to prime the
    learner for the content.
 2. `objectives` are the learning objectives for an episode displayed with
    the questions.
 3. `keypoints` are displayed at the end of the episode to reinforce the
    objectives.

:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::: instructor

Inline instructor notes can help inform instructors of timing challenges
associated with the lessons. They appear in the "Instructor View"

::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::: callout

You can create different section by using tags and fences

:::::::::::::::::::

::::::::::::::::::::::: testimonial

I'm always excited for **Mondays**, _so excited_.

-- No one ever

:::::::::::::::::::::::::::::::::::::::::


::::::::::::::::::::::::::::::::::::: challenge 

## Challenge 1: Can you do it?

What is the output of this command?

```r
paste("This", "new", "lesson", "looks", "good")
```

:::::::::::::::::::::::: solution 

## Output
 
```output
[1] "This new lesson looks good"
```

:::::::::::::::::::::::::::::::::


## Challenge 2: how do you nest solutions within challenge blocks?

:::::::::::::::::::::::: solution 

You can add a line with at least three colons and a `solution` tag.

:::::::::::::::::::::::::::::::::

::::::::::::::: solution

So this should be a second solution

::::::::::::::
::::::::::::::::::::::::::::::::::::::::::::::::


:::::::::::::::::::::::::: challenge

## Riddle me this

What can run but not walk?

:::::::::::::::::::: solution

A: A river!

::::::::::::::::::::
::::::::::::::::::::::::::

::::::::::::::::::::: my-class
This is a block of my class

:::::::::::::::::::::

Introducing Code Blocks
```
thing = "python"
print("this is a {} code block".format(thing))
```

```python
thing = "python"
print("this is a {} code block".format(thing))
```

```output
this is a python code block
```
##Tables try outs

Table: Eenie meenie minie mo

| first | second | title 3 |
| ----  | :--------------------: | ---- |
| this should be a small, compact column | this should be a wide column | this is another small compact column |

## Table with R Markdown

```{r fruits-table, results='asis'}
dat <- data.frame(
  stringsAsFactors = FALSE,
  fruit = c("apple", "pear", "orange", "devil"),
  color = c("red", "green", "orage_square", "purple_square"),
  price = c("£2.50", "£1.50", "£4.65", "£7.00"),
  description = c("tuffieha", "hadra hagu", "orange orange", "as you do")
)
knitr::kable(dat,
             format ="pipe",
             align = "lcrl",
             caption = "Testing out knitr with fruit")
```

# Link Reference

[link reference](http://github.com/annaliesemg/buoyant-barnacle)


## Figures

You can include figures generated from R Markdown:

```{r pyramid, fig.alt = "pie chart illusion of a pyramid", fig.cap = "Sun arise each and every morning"}
pie(
  c(Sky = 78, "Sunny side of pyramid" = 17, "Shady side of pyramid" = 5), 
  init.angle = 315, 
  col = c("deepskyblue", "yellow", "yellow3"), 
  border = FALSE
)
```
Or you can use pandoc markdown for static figures with the following syntax:

`![optional caption that appears below the figure](figure url){alt='alt text for
accessibility purposes'}`

![You belong in The Carpentries!](https://raw.githubusercontent.com/carpentries/logo/master/Badge_Carpentries.svg){alt='Blue Carpentries hex person logo with no text.'}

## Math

One of our episodes contains $\LaTeX$ equations when describing how to create
dynamic reports with {knitr}, so we now use mathjax to describe this:

`$\alpha = \dfrac{1}{(1 - \beta)^2}$` becomes: $\alpha = \dfrac{1}{(1 - \beta)^2}$

Cool, right?

::::::::::::::::::::::::::::::::::::: keypoints 

- Use `.md` files for episodes when you want static content
- Use `.Rmd` files for episodes when you need to generate output
- Run `sandpaper::check_lesson()` to identify any issues with your lesson
- Run `sandpaper::build_lesson()` to preview your lesson locally
- Put a neat summary in the keypoints section here

::::::::::::::::::::::::::::::::::::::::::::::::

